### 2023-10-03 2.State/lstm.tex
New figures and stuff

\begin{figure}[H]
  \centering
  \includesvg[width=\textwidth]{lstm/lstmCell.svg}
  \caption{LSTM Cell}
  \label{fig:lstmCell}
\end{figure}

\Cref{fig:lstmCell} shows the complexity of the \ac{LSTM} architecture. In an \ac{LSTM}, each gate is a different \ac{NN} and then activated with either a tanh or a sigmoid activation function. Each input to the cell is a vector.
Those vector are of varying sizes depending on several factors. For example, both $h_t$ and $c_t$ are of the same size as the number of hidden state (sometimes refered to as cell state) for any $t\geq 0$.
The input vector ($x_t$) is of size of the sample we want to feed for each time step.

@@

\begin{figure}[H]
  \centering
  \includesvg[width=\textwidth]{lstm/lstmUse}
  \caption{LSTM use case}
  \label{fig:lstmUse}
\end{figure}

>>>>

\begin{figure}[H]
  \centering
  \begin{minipage}{\columnwidth}
    \subfloat[\acs{LSTM} cell\label{fig:lstmCell}]{\includesvg[width=\textwidth,pretex=\large]{lstm/lstmCell.svg}}
  \end{minipage}
  \begin{minipage}{\columnwidth}
    \subfloat[Legend\label{leg:lstm}]{\includesvg[width=\textwidth,pretex=\large]{lstm/lstmLegend.svg}}
  \end{minipage}
  \caption{}
\end{figure}

\Cref{fig:lstmCell} shows the complexity of the \ac{LSTM} architecture. In an \ac{LSTM}, each gate is a different \ac{NN} and then activated with either a \ac{tanh} or a sigmoid activation function. Each input to the cell is a vector.
Those vector are of varying sizes depending on several factors. For example, both $h_t$ and $c_t$ are of the same size as the number of hidden state (sometimes refered to as cell state) for any $t\geq 0$.
The input vector ($x_t$) is of size of the sample we want to feed for each time step.

@@

\begin{figure}[H]
  \centering
  \includesvg[width=\textwidth]{lstm/lstmUse}
  \caption{LSTM use case, legend in \cref{leg:lstm}}
  \label{fig:lstmUse}
\end{figure}
